p-adic stability in linear algebra

### 2015-01-19 examples/stability.tex
Typo

Let $M_{m,n}(K)$ denote the space of $m \times n$ matrices over $K$.  We will repeatedly
use the Smith decomposition for $M \in M_{m,n}(K)$:
\[
M = U_M \cdot \Delta_M \cdot V_M,
\]
with $U_M$ and $V_M$ unimodular and $\Delta_M$ diagonal.  Write $\sigma_i(M)$
for the valuation of the $(i,i)$-th entry of $\Delta_M$, and by convention set
$\sigma_i(M) = +\infty$ if $i > \min(m,n)$.  Order the $\sigma_i(M)$ so that $\sigma_i(M) \le \sigma_{i+1}(M)$.

@@

Such polygons arise naturally in tracking the precision of polynomials 
\cite{caruso-roe-vaccon:14a}*{\S 4.2}.  Any such polygon $P$ yields a 
lattice $\mathcal{L}_P$ in $K_{<n}[X]$ consisting polynomials whose 
Newton polygons lie above $P$.  This lattice is generated by monomials 
$a_iX^i$, where $\val(a_i)$ is the ceiling of the height of $P$ at $i$.  
One uses these polygons to do a certain kind of coordinate-wise 
precision tracking for polynomials, bounding the actual precision 
lattice. We now introduce another polygon, bounded 
between these two, that will provide an estimate on the precision of $\charpoly(M)$.

>>>>

Let $M_{m,n}(K)$ denote the space of $m \times n$ matrices over $K$.  We will repeatedly
use the Smith decomposition for $M \in M_{m,n}(K)$:
\[
M = U_M \cdot \Delta_M \cdot V_M,
\]
with $U_M$ and $V_M$ unimodular and $\Delta_M$ diagonal.  Write $\sigma_i(M)$
for the valuation of the $(i,i)$th entry of $\Delta_M$, and by convention set
$\sigma_i(M) = +\infty$ if $i > \min(m,n)$.  Order the $\sigma_i(M)$ so that $\sigma_i(M) \le \sigma_{i+1}(M)$.

@@

Such polygons arise naturally in tracking the precision of polynomials 
\cite{caruso-roe-vaccon:14a}*{\S 4.2}.  Any such polygon $P$ yields a 
lattice $\mathcal{L}_P$ in $K_{<n}[X]$ consisting of polynomials whose 
Newton polygons lie above $P$.  This lattice is generated by monomials 
$a_iX^i$, where $\val(a_i)$ is the ceiling of the height of $P$ at $i$.  
One uses these polygons to do a certain kind of coordinate-wise 
precision tracking for polynomials, bounding the actual precision 
lattice. We now introduce another polygon, bounded 
between these two, that will provide an estimate on the precision of $\charpoly(M)$.
